---
title: "Programming Background"
author: "Kristi Ramey"
date: "9/14/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")
```

## Programming Background

Back when I was a wee-undergrad, I took one intro to programming course for my math major which used the language C++.  I remember fondly my professor, who had the same exact tonality of Bill Cosby (back before Bill Cosby was known as a predator), and he had the idiosyncrasy of wiping the chalk board clean meticulously in long swipes, end to end.  I also remember the countless hours I spent on my final project where I had to write a program to simulate booking passengers at an airport.  The reason my project turned into an odyssey was that I had failed to add ‘+1’ to my counter, so my code went off to an oblivion of zeros and ones and kept crashing my computer.  Thus started my love of computer science.  
Fast forward to entering into the Master’s program in Statistics at NC State…
While this course is my first exposure to intense programming with R, I had dabbled in R labs in previous course.  Most of those ‘toe dipping’ experiences were following the professor’s code, line by line and changing one or two fields to fit the problem.  Overall, it was a nice experience, but I did have several instances where the professor underestimated my dependance on their examples and was left in a tizzy when the file or operation deviated one step past the provided code.
While I wouldn’t say I enjoy R, I now have a deeper appreciation.  I like the rather simple structure of vectors, matrices, data frames, and lists.  I LOVE the help resources with R that are available on-line.  Since it is open-sourced, it feels more of a community where people will post questions and get rather straightforward responses.  I was a kumquat and fought off R Markdown until this course and now I see its full glory!  No more screen clipping code and adding them to a OneNote page.  My professor has mentioned numerous times that the best and worst thing is most things have multiple ways to code it in.  
I also have had two courses that used SAS instead of R.  My impression of SAS was a pal that made you buy their Amway products.  It’s been a full year since SAS coding, but I remember it as being very straightforward with no CasE iSSues to worry about and semi-colons everywhere.  Truth be told, that might have been the result of a ton handholding by the professor.  I do remember feeling defeated by the installation process.  I had to call Tech Support, where the person had to take over my computer to install it.  Why the issue, you ask?  Because my work computer used ‘D:’ as the personal directory, instead of the more common ‘C:’.  I also remember my license expiring right as a project was due, which gave me more adrenaline than was needed.
Of the two languages, I prefer R, which is why I waited NC State out for them to remove the ST555 requirement for Master candidates (an intensive SAS course).  While that gave me one less language to struggle with, it came at a cost.  I wish I had taken my program intensive course sooner, since it would have given me more confidence and knowledge with R, before the concepts became intense.  But, se la vie, I’m glad I’m in this course now.  

## Example R Markdown output.
```{r }
plot(iris)
```
